---
title: "project"
author: "Hakan Ekiz/Batuhan Tunçel/Yusuf Beşiroğlu - IE48B - Fall2021"
date: "24 January 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
require(data.table)
require(ggplot2)
require(repr)
require(rpart)
require(rattle)
require(TSrepr)
require(TSdist)
require(dtw)
require(zoo)
require(genlasso)
require(e1071)
require(lubridate)
require(forecast)
require(dplyr)
```

```{r}
options(repr.plot.width=15, repr.plot.height=8)

current_folder=getwd()
```

---
The latest input <br>
```{r}

dat=fread('bulk_imbalance.csv')
weat=fread('2022-01-21_weather.csv')
head(dat)
head(weat)

```


```{r}

c1 = dat
c1 = c1[,list(date,hour,net,system_direction)]
c1[,datetime:=ymd(date)+dhours(hour)]
c1=c1[order(datetime)]

c2 = c1[,list(datetime,net,system_direction)]
c2


```



```{r}
w1 = weat
w1[,datetime:=ymd(date)+dhours(hour)]
w1=w1[order(datetime)]
w1

```

Ordering by date-time for all locations and their weather conditions <br>
Also bringing all parameters together <br>
```{r}
w1 = w1 %>% 
  mutate(loc = 
           case_when(lat <= 36.50 ~ "loc1" ,
                     lat==37.00 ~ "loc2" ,
                     lat==38.00 ~ "loc3" ,
                     lat==38.50 ~ "loc4" ,
                     lat==39.75 ~ "loc5" ,
                     lat==40.00 ~ "loc6" ,
                     lat>=41.00 ~ "loc7" )
         )
w1= as.data.table(w1)
w1
```


```{r}

w1[,class:=paste(loc,variable)]
w1

```




```{r}

w2 = w1[,list(datetime,class,value)]
w2[,class:=as.factor(class)]
w2
```


```{r}
trainw2=dcast(w2[!is.na(value)],datetime~class,value.var='value')
trainw2
```

```{r}
names(trainw2) <- gsub(" ", "_", names(trainw2))
trainw2
```



```{r}

all = merge(c2,trainw2, by="datetime")
all
```


```{r}
ggplot(all ,aes(x=datetime,y=net)) + geom_line()
```


```{r}
all[,trnd:=1:.N]

all[,w_day:=as.character(wday(datetime,label=T))]
all[,mon:=as.character(month(datetime,label=T))]
all[,hour:=as.factor(hour(datetime))]
all[,Date:=as.Date(datetime)]
all
```



First linear regression uses all parameters and it's our baseline <br>
```{r}

lm1=lm(net~trnd+w_day+mon+hour+
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_TMP_2.m.above.ground+loc1_wdir_10m+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc1_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_TCDC_low.cloud.layer+loc3_TMP_2.m.above.ground+loc3_wdir_10m+loc1_ws_10m+
         loc4_DSWRF_surface+loc4_RH_2.m.above.ground+loc4_TCDC_low.cloud.layer+loc4_TMP_2.m.above.ground+loc4_wdir_10m+loc1_ws_10m+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_TMP_2.m.above.ground+loc5_wdir_10m+loc1_ws_10m+
         loc6_DSWRF_surface+loc6_RH_2.m.above.ground+loc6_TCDC_low.cloud.layer+loc6_TMP_2.m.above.ground+loc6_wdir_10m+loc1_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer+loc7_TMP_2.m.above.ground+loc7_wdir_10m+loc1_ws_10m
       ,all)


summary(lm1)


```

```{r}
tmp=copy(all)
tmp[,actual:=net]
tmp[,predicted:=predict(lm1,tmp)]
#head(tmp)
ggplot(tmp[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```

```{r}
lm2=lm(net~trnd+w_day+mon+hour,all)
summary(lm2)
```

```{r}
tmp2=copy(all)
tmp2[,actual:=net]
tmp2[,predicted:=predict(lm2,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```

```{r}
checkresiduals(lm2$residuals)

```

```{r}
tmp2[,prevday:=shift(x=tmp2$net,n=24L,fill=mean(tmp2$net))]
tmp2[,prevweek:=shift(x=tmp2$net,n=168L,fill=mean(tmp2$net))]
tmp2
```

After that try 13 linear regression to reach better results<br>
```{r}
lm2_1=lm(net~trnd+w_day+mon+hour+prevday+prevweek,
                 tmp2)
summary(lm2_1)
```

```{r}
tmp2[,predicted:=predict(lm2_1,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```



```{r}


tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~w_day+mon+hour+prevday+prevweek+
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_TMP_2.m.above.ground+loc1_wdir_10m+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_TCDC_low.cloud.layer+loc3_TMP_2.m.above.ground+loc3_wdir_10m+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_RH_2.m.above.ground+loc4_TCDC_low.cloud.layer+loc4_TMP_2.m.above.ground+loc4_wdir_10m+loc4_ws_10m+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_TMP_2.m.above.ground+loc5_wdir_10m+loc5_ws_10m+
         loc6_DSWRF_surface+loc6_RH_2.m.above.ground+loc6_TCDC_low.cloud.layer+loc6_TMP_2.m.above.ground+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer+loc7_TMP_2.m.above.ground+loc7_wdir_10m+loc7_ws_10m,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```


```{r}

tmp2[,loc7tmp2ag:=as.numeric(loc7_TMP_2.m.above.ground>=30)]
tmp2[,pv:=as.numeric(prevweek>=2070)]
tmp2[,loc7tmp2ag2:=as.numeric(loc7_TMP_2.m.above.ground>=31)]

lm2_2=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2,
                 tmp2)
summary(lm2_2)



```


```{r}

tmp2[,predicted:=predict(lm2_2,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```


```{r}


tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~w_day+mon+hour+prevday+prevweek+
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_TMP_2.m.above.ground+loc1_wdir_10m+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_TCDC_low.cloud.layer+loc3_TMP_2.m.above.ground+loc3_wdir_10m+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_RH_2.m.above.ground+loc4_TCDC_low.cloud.layer+loc4_TMP_2.m.above.ground+loc4_wdir_10m+loc4_ws_10m+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_TMP_2.m.above.ground+loc5_wdir_10m+loc5_ws_10m+
         loc6_DSWRF_surface+loc6_RH_2.m.above.ground+loc6_TCDC_low.cloud.layer+loc6_TMP_2.m.above.ground+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer+loc7_wdir_10m+loc7_ws_10m,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```


```{r}

tmp2[,loc5tmp2ag:=as.numeric(loc5_TMP_2.m.above.ground>=29)]
tmp2[,pd:=as.numeric(prevday>=2329)]
tmp2[,workday:=as.numeric(!w_day %in% c('Cmt','Paz'))]

lm2_3=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday,
                 tmp2)
summary(lm2_3)



```



```{r}

tmp2[,predicted:=predict(lm2_3,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```


```{r}
tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~mon+hour+
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_TMP_2.m.above.ground+loc1_wdir_10m+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_TCDC_low.cloud.layer+loc3_TMP_2.m.above.ground+loc3_wdir_10m+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_RH_2.m.above.ground+loc4_TCDC_low.cloud.layer+loc4_TMP_2.m.above.ground+loc4_wdir_10m+loc4_ws_10m+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+loc5_ws_10m+
         loc6_DSWRF_surface+loc6_RH_2.m.above.ground+loc6_TCDC_low.cloud.layer+loc6_TMP_2.m.above.ground+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer+loc7_wdir_10m+loc7_ws_10m,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```


```{r}

tmp2[,loc4tmp2ag:=as.numeric(loc4_TMP_2.m.above.ground<8.6)]
tmp2[,whour:=as.numeric(as.numeric(hour)<9 | as.numeric(hour)>18)]
tmp2[,loc3wdir:=as.numeric(loc3_wdir_10m<336)]

lm2_4=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir,
                 tmp2)
summary(lm2_4)



```



```{r}

tmp2[,predicted:=predict(lm2_4,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```


```{r}

tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~mon+
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_TMP_2.m.above.ground+loc1_wdir_10m+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_TCDC_low.cloud.layer+loc3_TMP_2.m.above.ground+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_RH_2.m.above.ground+loc4_TCDC_low.cloud.layer+loc4_wdir_10m+loc4_ws_10m+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+loc5_ws_10m+
         loc6_DSWRF_surface+loc6_RH_2.m.above.ground+loc6_TCDC_low.cloud.layer+loc6_TMP_2.m.above.ground+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer+loc7_wdir_10m+loc7_ws_10m,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```

```{r}

tmp2[,loc6tmp2ag:=as.numeric(loc6_TMP_2.m.above.ground>=26)]
tmp2[,loc7ws:=as.numeric(loc7_ws_10m<3)]
tmp2[,loc1wdir:=as.numeric(loc1_wdir_10m>=172)]

lm2_5=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir,
                 tmp2)
summary(lm2_5)


```

```{r}
tmp2[,predicted:=predict(lm2_5,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```


```{r}

tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~mon+
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_TMP_2.m.above.ground+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_TCDC_low.cloud.layer+loc3_TMP_2.m.above.ground+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_RH_2.m.above.ground+loc4_TCDC_low.cloud.layer+loc4_wdir_10m+loc4_ws_10m+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+loc5_ws_10m+
         loc6_DSWRF_surface+loc6_RH_2.m.above.ground+loc6_TCDC_low.cloud.layer+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer+loc7_wdir_10m,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```

```{r}

tmp2[,loc4wdir:=as.numeric(loc4_wdir_10m<170)]
tmp2[,loc7wdir:=as.numeric(loc7_wdir_10m>=214)]
tmp2[,loc3tmp2ag:=as.numeric(loc3_TMP_2.m.above.ground>=20)]

lm2_6=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir
         +loc4wdir:loc7wdir+loc3tmp2ag,
                 tmp2)
summary(lm2_6)


```

```{r}
tmp2[,predicted:=predict(lm2_6,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```

```{r}

tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~mon+
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_TMP_2.m.above.ground+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_TCDC_low.cloud.layer+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_RH_2.m.above.ground+loc4_TCDC_low.cloud.layer+loc4_ws_10m+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+loc5_ws_10m+
         loc6_DSWRF_surface+loc6_RH_2.m.above.ground+loc6_TCDC_low.cloud.layer+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```



```{r}

tmp2[,loc3tcdc:=as.numeric(loc3_TCDC_low.cloud.layer>=8.6)]
tmp2[,mon1:=as.numeric(!mon %in% c('Haz','Tem','Ağu','Eyl','Eki'))]
tmp2[,loc4rh:=as.numeric(loc4_RH_2.m.above.ground<69)]

lm2_7=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir
         +loc4wdir:loc7wdir+loc3tmp2ag+loc3tcdc:mon1:loc4rh,
                 tmp2)
summary(lm2_7)


```

```{r}
tmp2[,predicted:=predict(lm2_7,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```


```{r}

tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_TMP_2.m.above.ground+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_TCDC_low.cloud.layer+loc4_ws_10m+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+loc5_ws_10m+
         loc6_DSWRF_surface+loc6_RH_2.m.above.ground+loc6_TCDC_low.cloud.layer+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```


```{r}

tmp2[,loc4ws:=as.numeric(loc4_ws_10m<3.5)]
tmp2[,loc6rh:=as.numeric(loc6_RH_2.m.above.ground<40)]
tmp2[,loc1tmp2ag:=as.numeric(loc1_TMP_2.m.above.ground>=15)]

lm2_8=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir
         +loc4wdir:loc7wdir+loc3tmp2ag+loc3tcdc:mon1:loc4rh+loc4ws:loc6rh:loc1tmp2ag,
                 tmp2)
summary(lm2_8)


```

```{r}
tmp2[,predicted:=predict(lm2_8,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```
```{r}

tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_TMP_2.m.above.ground+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_TCDC_low.cloud.layer+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+loc5_ws_10m+
         loc6_DSWRF_surface+loc6_TCDC_low.cloud.layer+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_RH_2.m.above.ground+loc7_TCDC_low.cloud.layer,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```


```{r}

tmp2[,loc5ws:=as.numeric(loc5_ws_10m<2.4)]
tmp2[,loc2tmp2ag:=as.numeric(loc2_TMP_2.m.above.ground<2.3)]
tmp2[,loc7rh2:=as.numeric(loc7_RH_2.m.above.ground<63)]

lm2_9=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir
         +loc4wdir:loc7wdir+loc3tmp2ag+loc3tcdc:mon1:loc4rh+loc4ws:loc6rh:loc1tmp2ag+loc5ws:loc2tmp2ag:loc7rh2,
                 tmp2)
summary(lm2_9)


```

```{r}
tmp2[,predicted:=predict(lm2_9,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```


```{r}

tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+loc1_ws_10m+
         loc2_DSWRF_surface+loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_TCDC_low.cloud.layer+
         loc5_DSWRF_surface+loc5_RH_2.m.above.ground+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+
         loc6_DSWRF_surface+loc6_TCDC_low.cloud.layer+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_TCDC_low.cloud.layer,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```


```{r}

tmp2[,loc5rh:=as.numeric(loc5_RH_2.m.above.ground<16)]
tmp2[,loc1ws:=as.numeric(loc1_ws_10m>=3.9)]
tmp2[,loc2dswrf:=as.numeric(loc2_DSWRF_surface<841)]

lm2_10=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir
         +loc4wdir:loc7wdir+loc3tmp2ag+loc3tcdc:mon1:loc4rh+loc4ws:loc6rh:loc1tmp2ag+loc5ws:loc2tmp2ag:loc7rh2+loc5rh:loc1ws:loc2dswrf,
                 tmp2)
summary(lm2_10)




```

```{r}
tmp2[,predicted:=predict(lm2_10,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```


```{r}

tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~
         loc1_DSWRF_surface+loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+
         loc2_RH_2.m.above.ground+loc2_TCDC_low.cloud.layer+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_TCDC_low.cloud.layer+
         loc5_DSWRF_surface+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+
         loc6_DSWRF_surface+loc6_TCDC_low.cloud.layer+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_TCDC_low.cloud.layer,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```

```{r}

tmp2[,loc6tcdc:=as.numeric(loc6_TCDC_low.cloud.layer>=84)]
tmp2[,loc1dswrf:=as.numeric(loc1_DSWRF_surface>=90)]
tmp2[,loc2rh2:=as.numeric(loc2_RH_2.m.above.ground>=91)]

lm2_11=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir
         +loc4wdir:loc7wdir+loc3tmp2ag+loc3tcdc:mon1:loc4rh+loc4ws:loc6rh:loc1tmp2ag+loc5ws:loc2tmp2ag:loc7rh2+loc5rh:loc1ws:loc2dswrf
         +loc6tcdc:loc1dswrf:loc2rh2,
                 tmp2)
summary(lm2_11)


```

```{r}
tmp2[,predicted:=predict(lm2_11,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))
```


```{r}

tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~
         loc1_RH_2.m.above.ground+loc1_TCDC_low.cloud.layer+
         loc2_TCDC_low.cloud.layer+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+loc3_ws_10m+
         loc4_DSWRF_surface+loc4_TCDC_low.cloud.layer+
         loc5_DSWRF_surface+loc5_TCDC_low.cloud.layer+loc5_wdir_10m+
         loc6_DSWRF_surface+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_TCDC_low.cloud.layer,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)

```

```{r}

tmp2[,loc3ws:=as.numeric(loc3_ws_10m<1.1)]
tmp2[,loc1tcdc:=as.numeric(loc1_TCDC_low.cloud.layer>=63)]
tmp2[,loc5wdir:=as.numeric(loc5_wdir_10m<69)]

lm2_12=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir
         +loc4wdir:loc7wdir+loc3tmp2ag+loc3tcdc:mon1:loc4rh+loc4ws:loc6rh:loc1tmp2ag+loc5ws:loc2tmp2ag:loc7rh2+loc5rh:loc1ws:loc2dswrf
         +loc6tcdc:loc1dswrf:loc2rh2+loc3ws:loc1tcdc:loc5wdir,
                 tmp2)
summary(lm2_12)


```

```{r}
tmp2[,predicted:=predict(lm2_12,tmp2)]
#head(tmp)
ggplot(tmp2[Date=='2019-05-08'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))




```

```{r}
tmp2[,residual:=actual-predicted]


fit_res_tree=rpart(residual~
         loc1_RH_2.m.above.ground+
         loc2_TCDC_low.cloud.layer+loc2_wdir_10m+loc2_ws_10m+
         loc3_DSWRF_surface+loc3_RH_2.m.above.ground+
         loc4_DSWRF_surface+loc4_TCDC_low.cloud.layer+
         loc5_DSWRF_surface+loc5_TCDC_low.cloud.layer+
         loc6_DSWRF_surface+loc6_wdir_10m+loc6_ws_10m+
         loc7_DSWRF_surface+loc7_TCDC_low.cloud.layer,tmp2,
                   control=rpart.control(cp=0,maxdepth=3))

fancyRpartPlot(fit_res_tree)
```

After comparision between models, deciding to continue with the 13th model <br>
Submit results depends on this model <br>
```{r}
tmp2[,loc3rh:=as.numeric(loc3_RH_2.m.above.ground<25)]
tmp2[,loc5tcdc:=as.numeric(loc5_TCDC_low.cloud.layer<0.15)]
tmp2[,loc1rh:=as.numeric(loc1_RH_2.m.above.ground>=15)]

lm2_13=lm(net~trnd+w_day+mon+hour+prevday+prevweek+loc7tmp2ag:pv:loc7tmp2ag2+loc5tmp2ag:pd:workday+loc4tmp2ag:whour:loc3wdir+loc6tmp2ag:loc7ws:loc1wdir
         +loc4wdir:loc7wdir+loc3tmp2ag+loc3tcdc:mon1:loc4rh+loc4ws:loc6rh:loc1tmp2ag+loc5ws:loc2tmp2ag:loc7rh2+loc5rh:loc1ws:loc2dswrf
         +loc6tcdc:loc1dswrf:loc2rh2+loc3ws:loc1tcdc:loc5wdir+loc3rh:loc5tcdc:loc1rh,
                 tmp2)
summary(lm2_13)

tmp2[,predicted:=predict(lm2_13,tmp2)]

```

```{r}
checkresiduals(lm2_13$residuals)

```

```{r}

tmp2[,residuals13 := residuals(lm2_13)]
acf(residuals(lm2_13) , lag.max = 160)


```

```{r}
ggplot(tmp2[Date=='2022-01-07'] ,aes(x=datetime)) +
        geom_line(aes(y=actual,color='real')) + 
        geom_line(aes(y=predicted,color='predicted'))

```





```{r}
tmp2 = tmp2 %>% 
  mutate(predicted_diretion = 
           case_when(predicted < -50 ~ "Negative" ,
                     predicted>=-50 & predicted<=50 ~ "Neutral" ,
                     predicted> 50 ~ "Positive" )
         )
tmp2= as.data.table(tmp2)
tmp2
```

```{r}
submission = tmp2[,list(Date,hour,system_direction,predicted_diretion)]
tail(submission,12)
```





